Manuscript draft

### 2019-08-07 manuscript/manuscript draft.Rmd
updated manuscript draft

Including a second climate term in the models tended to have only a small effect on the explanatory power of the models. For ANPP~woody stem~ and R~auto~, including two climate terms did not improve the explantory power of the models: mean annual temperature alone was the best climate predictor for both of these fluxes. For all the remaining carbon fluxes, including a second climate term did improve the explanatory power of the models. ANPP and ANPP~foliage~ were best explained by an additive model, in both cases including mean annual temperature and potential evapotranspiration as the climate terms. GPP, NPP, BNPP, BNPP~fine root~, and R~root~ were all best explained by multivariate models which included an interaction term between the two climate terms. The best models for GPP, NPP, and R~root~ all included a temperature term and a precipitation term, indicating that although precipitation isn't a strong predictor for these variables, the interaction between temperature and water availability is important.

@@

>>>>

There was a significant interactive effect between MAT and MAP for GPP, BNPP~root~, BNPP~fine root~, ANPP, ANPP~woody stem~, and R~root~. There was a significant additive effect for R~auto~. NPP and ANPP~foliage~ showed no significant interactive or additive effect: including MAP as a second variable did not improve on the model including only MAT.

For the variables which showed a significant interactive or additive effect between MAT and MAP, no other climate variable, in combination with MAT, significantly improved on that model. For NPP, there was a significant interactive effect between MAT and water stress months, with this model explaining nearly 5% more variation in NPP than MAT alone. However, for ANPP~foliage~, no multivariate model improved on the univariate model including only MAT.

@@

*The relationship between productivity and latitude*

Past studies have differed in their conclusions regarding the relationship between productivity and latitude. Our findings indicate that, for all carbon fluxes studied, productivity peaks in the tropical regions. While Huston and Wolverton (2009) found no significant relationship between ANPP and latitude, we find a significant negative relationship between ANPP and latitude, with the highest levels of ANPP in the tropical regions.
